25 years of Social Work Research

### 2015-03-28 dataCleaning.Rmd
Lots of updates ...

```{r initialization}
rm(list=ls())  
#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")

@@

```{r}
save.image(file = "socialWorkHistory.Rdata")
```

@@

```{r}
mapCountryData(spdf, nameColumnToPlot="frequency", catMethod="quantiles", 
                                  colourPalette="white2Black", 
                                  mapTitle="Article Countss by Country, 1989-2013")
```

>>>>

```{r initialization}
rm(list=ls())  
load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")

@@

```{r eval=FALSE}
save.image(file = "socialWorkHistory.Rdata")
```

@@

```{r}
mapCountryData(spdf, nameColumnToPlot="frequency", catMethod="quantiles", 
                                  colourPalette="white2Black", 
                                  mapTitle="Article Counts by Country, 1989-2013")
```
